\cvsection{Work Experience}

\begin{cventries}

    \cventry
    {Senior Software Engineer - Data Solutions}
    {H-E-B Grocery, LP}
    {Remote}
    {Apr. 2024 - Present}
    {
        \begin{cvitems}
            \item {Develop multi-representation architecture for heterogenous pub-sub consumers on top of Python and Kafka.}
            \item {Allowed records in SQL, Delta Lake, S3, or Kafka topics to be represented in other formats, as well as backing a REST API.}
            \item {Configuration DSL based on jq allowed for remapping objects or executing SQL against DeltaTables.}
            \item {Productionalize and refactor AI models in a cross-team setting as Data Engineer.}
            \item {Greenfield ML projects with online feedback for search ranking to drive customer engagement 2-3\%.}
        \end{cvitems}
    }

    \cventry
    {Lead Developer - Backend Microservice Platform}
    {DefenseStorm, Inc.}
    {Remote}
    {Nov. 2022 - Apr. 2024}
    {
        \begin{cvitems}
            \item {Rewrote sequential workers as event-based workflow with parallelized execution.}
            \item {Enabled machine learning teams to incorporate alert detection models in alert generation by leveraging push-driven workflow.}
            \item {Rewrote notification logic to prevent degradations in external services from impacting core alerting stability and improve customer visible KPIs.}
            \item {Designed schemas, performed task breakdowns, and architected projects for a team of developers.}
        \end{cvitems}
    }

    \cventry
    {Senior Software Engineer}
    {} % Empty Org Name
    {} % Empty Location
    {Jan. 2021 - Nov. 2022}
    {
        \begin{cvitems}
            \item {Improved internal only service API structure to develop a customer integratable public API, with authorization and authentication.}
            \item {Developed near real-time, event-driven fraud detection framework; optimized using SQS, multi-threading and Java Promise APIs.}
            %\item {Halved build times in distributed log processing service by optimizing code and dependencies.}
            \item {Migrated existing U2F login support to WebAuthn seamlessly. \href{https://www.jacobcasper.com/u2f2webauthn.html}{Blog post}}
            %\item {Optimize API requests that cannot fit in service memory by utilizing streaming REST requests.}
            %\item {Develop distributed request tracing for observability.}
        \end{cvitems}
    }

	\cventry
	{Software Developer}
	{IBM - SoftLayer}
	{Dallas, Texas}
	{Apr. 2018 - Jan. 2021}
	{
		\begin{cvitems}
			\item {Created a distributed worker architecture using RabbitMQ that reduced runtime of a 20-hour batch process to minutes.}
			\item {Enabled process visibility and communication between distributed services by creating a message passing framework.}
			\item {Designed alerting tool for Continuous Integration by scripting git internals to detect exact commit responsible for a test suite regression.}
			%\item {Developed Influx queries for anomaly detection in API submissions to prevent revenue losses of \$1m/month.}
			%\item {Scaled billing systems that process billions of USD worth of customer transactions.}
%           \item {Integrate and consume third party web services.}
%			\item {Implement tooling to automate billing processes.}
		\end{cvitems}
	}
	
%\cventry
%	{Software Engineer Intern} % Job title
%	{IBM} % Organization
%	{Raleigh, North Carolina} % Location
%	{May 2017 - Aug. 2017} % Date(s)
%	{
%		\begin{cvitems} % Description(s) of tasks/responsibilities
%			\item {Migrated Build Verification Testing (BVT) pipeline to Jenkins Automation tools.}
%			\item {Managed operations for virtual and physical machines used in testing environment.}
%		\end{cvitems}
%	}
%	
%\cventry
%	{Software Engineer Intern} % Job title
%	{IBM} % Organization
%	{Raleigh, North Carolina} % Location
%	{May 2016 - Aug. 2016} % Date(s)
%	{
%		\begin{cvitems} % Description(s) of tasks/responsibilities
%			\item {Worked with server analytics, logging, and client migrations across multiple sets of
%				hardware.}
%			\item {Worked in and maintained sandboxed development environments.}
%		\end{cvitems}
%	}

%\cventry
%	{Quality Assurance/Control and Product Development/Testing} % Job title
%	{JANUS Research Group} % Organization
%	{Fayetteville, North Carolina} % Location
%	{Jun. 2014 - Aug. 2014} % Date(s)
%	{
%		\begin{cvitems} % Description(s) of tasks/responsibilities
%			\item {Consultant on Serious Game Technology and Serious Game Design.}
%			\item {Quality Assurance/Control and bug testing and squashing for Serious Games, Web Development, and IMI Virtual Training.}
%		\end{cvitems}
%	}

\end{cventries}
